---
title: "Course 2 Weekly Quiz 1"
author: "Zhenzhuo A. C."
date: "25.03.22"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
result: 90/100
---


#### Question 3. In R the following are all *atomic data* types EXCEPT:

- **Answer**: Array, list, data frame, matrix, table  
- **PS**: use class() function can help you identify the data type



#### Question 4. If I execute the expression x <- 4 in R, what is the class of the object `x'?
```{r}
x <- 4
class(x)
```
- **Answer**: numeric



#### Question 5. What is the class of the object defined by the expression x <- c(4, "a", TRUE)?
```{r}
x <- c(4, "a", TRUE)
class(x)
```
- **Answer**: character



#### Question 6: If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)?
```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
rbind(x,y)
```
- **Answer**: This is a 2*3 matrix.

Additionally, with cbind(x,y)
```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
cbind(x,y)
```
- **Answer**: We can get a 3*2 matrix.



#### Question 7: A key property of vectors in R is that
- **Answer**: Elements of a vector all must be of the same class



#### Question 8: Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[2]] give me? Select all that apply.
```{r}
x <- list(2, "a", "b", TRUE)
x[[2]]
```
- **Answer**: A character vector containing the letter "a".



#### Question 9: Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?
```{r}
x <- 1:4
y <- 2
x+y
```

- **Answer**: 1:4 means 1 or 2 or 3 or 4. The answer is a numeric vector with elements 3, 4, 5, 6.A numeric vector with elements 3, 4, 5, 6.



#### Question 10: Suppose I have a vector x <- c(17, 14, 4, 5, 13, 12, 10) and I want to set all elements of this vector that are greater than 10 to be equal to 4. What R code achieves this? Select all that apply.
```{r}
x <- c(17, 14, 4, 5, 13, 12, 10)
x[x > 10] <- 4
```
- **Answer**: assign for under the requirement given in []



#### Question 12: Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
dataset1 <- read.csv("/Users/zhenzhuo.chen/Desktop/hw1_data.csv")
dataset1[1:2,]
```
- **PS**: See this example for extracting specific columns from a dataset. Do not forget the comma.



#### Question 13:How many observations (i.e. rows) are in this data frame?
```{r}
nrow(dataset1)
```
- **Answer**: 153
- **PS**: Use fuction nrow() with dataset_name to count the number of rows in a dataset.



#### Question 14: Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
dataset1[152:153,]
```



#### Question 15: What is the value of Ozone in the 47th row?
```{r}
dataset1$Ozone[47]
```
- Answer: 21
- **PS**: Dataset_name$column[number_of_the_row]. Using $ to select a specific column.



#### Question 16: How many missing values are in the Ozone column of this data frame?
```{r}
sum(is.na(dataset1$Ozone))
```
- **Answer**: 37
- **PS**: Use sum(is.na(dataset_nname)) to count missing values.

#### Question 17: What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(dataset1$Ozone, na.rm=TRUE)
```
- **Answer**: 42.12931
- **PS**: na.rm() is the function to remove missing values NA in the calculation.


#### Question 18：Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
library(dplyr)
subset_dataset1<-dataset1 %>%
  filter(dataset1$Ozone > 31, Temp>90)
mean(subset_dataset1$Solar.R)
```
- **Answer**: 212.8
- **PS**: I created a new data frame with filter() function from the dplyr package.


#### Question 19: What is the mean of "Temp" when "Month" is equal to 6? 
```{r}
mean(dataset1[which(dataset1$Month == 6),]$Temp)
```
- **Answer**: 79.1
- **PS**: which() is a very powerful function that prevents extra steps of creating a new data frame.


#### Question 20: What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
max(dataset1[which(dataset1$Month==5),]$Ozone, na.rm = TRUE)
```
- **Answer**: 115